### 2015-04-22 paper.tex
Add strut torque figure
Add perf covers figure

\begin{figure}[h]
%\includegraphics[width=\textwidth]{figures/cp_curves}
\caption{{\bf Power Coefficient Curves.}
Mean rotor power coefficient plotted versus mean tip speed ratio for multiple
Reynolds numbers.}
\label{fig:cp-curves}
\end{figure}

\begin{figure}[h]
%\includegraphics[width=\textwidth]{figures/cd_curves}
\caption{{\bf Drag Coefficient Curves.}
Mean rotor drag coefficient plotted versus mean tip speed ratio for multiple
Reynolds numbers.}
\label{fig:cd-curves}
\end{figure}

@@

\begin{figure}[h]
%\includegraphics[width=\textwidth]{figures/re_dep_cp}
\caption{{\bf Power Coefficient Reynolds Number Dependence.}
Power coefficient at $\lambda=3.1$ plotted versus Reynolds number.}
\label{fig:cp-re-dep}
\end{figure}

@@

\begin{figure}[h]
%\includegraphics[width=\textwidth]{figures/meancontquiv}
\caption{{\bf Near-Wake Mean Velocity Field.}
Mean velocity field at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
$\lambda=3.1$.}
\label{fig:meancontquiv}
\end{figure}

@@

\begin{figure}[h]
%\includegraphics[width=\textwidth]{figures/k_contours}
\caption{{\bf Turbulence Kinetic Energy.}
Turbulence kinetic energy at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
$\lambda=3.1$.}
\label{fig:kcont}
\end{figure}

@@

\begin{figure}[ht!]
%\includegraphics[width=\textwidth]{figures/K_trans_bar_graph}
\caption{{\bf Mean Kinetic Energy Transport.}
Estimates for terms contributing to streamwise recovery of mean kinetic energy.}
\label{fig:Ktransport}
\end{figure}

@@

>>>>

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/cp_curves}
\caption{{\bf Power Coefficient Curves.}
Mean rotor power coefficient plotted versus mean tip speed ratio for multiple
Reynolds numbers.}
\label{fig:cp-curves}
\end{figure}

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/cd_curves}
\caption{{\bf Drag Coefficient Curves.}
Mean rotor drag coefficient plotted versus mean tip speed ratio for multiple
Reynolds numbers.}
\label{fig:cd-curves}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/re_dep_cp}
\caption{{\bf Power Coefficient Reynolds Number Dependence.}
Power coefficient at $\lambda=3.1$ plotted versus Reynolds number.}
\label{fig:cp-re-dep}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/meancontquiv}
\caption{{\bf Mean Velocity.}
Mean velocity field at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
$\lambda=3.1$.}
\label{fig:meancontquiv}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/k_contours}
\caption{{\bf Turbulence Kinetic Energy.}
Turbulence kinetic energy at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
$\lambda=3.1$.}
\label{fig:kcont}
\end{figure}

@@

\begin{figure}[ht!]
\includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph}
\caption{{\bf Mean Kinetic Energy Transport.}
Estimates for terms contributing to streamwise recovery of mean kinetic energy.}
\label{fig:Ktransport}
\end{figure}

@@

\begin{figure}[ht!]
\includegraphics[width=\textwidth]{figures/no_blades_all}
\caption{{\bf Strut drag losses.}
Measurements of the strut drag losses for (a) NACA 0021 and (b) cylindrical 
struts, both stationary and towed.}
\label{fig:no-blades}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\textwidth]{figures/perf_covers}
\caption{{\bf High drag strut performance.}
Turbine performance and rotor drag coefficient curves with both NACA 0021
and cylindrical struts.}
\label{fig:perf-covers}
\end{figure}
